\subsection{Rules to avoid common mistakes}

All these rules are under category
\cppid{bugprone}.

\subsubsection{Applicable rules}

Below, main applicable rules are described.
Please, note that there are many more rules from this category that are enabled.
If you need a detailed explanation, you can consult the \cppkey{clang-tidy} manual. 

\begin{itemize}

\item \cppid{bugprone-assert-side-effect}:
Side effects in assertion evaluation (with \cppid{assert()}) shall be avoided.
This rule also applies to side effects with assertions from \textmark{GSL}:
\cppid{Expects} y \cppid{Ensures}.

The following option shall be used:
\begin{lstlisting}
bugprone-assert-side-effect.AssertMacros: 'assert,Expects,Ensures'
\end{lstlisting}

\item \cppid{bugprone-assignment-in-if-condition}:
No assignment shall be performed inside the condition of an \cppkey{if} statement.

\item \cppid{bugprone-casting-through-void}:
No conversion involving \cppkey{void*} shall be performed.

\item \cppid{bugprone-chained-comparison}:
No chained comparison that might be confusing shall be used.

\item \cppid{bugprone-easily-swappable-parameters}: 
No function shall have consecutive parameters from the same type that 
might lead to confusion.

\item \cppid{bugprone-implicit-widening-of-multiplication-result}: 
A \cppkey{static\_cast<>} shall be used to convert to an integral wider type.
If needed header \cppid{<cstddef>} shall be included.

The following option shall be used:
\begin{lstlisting}
bugprone-implicit-widening-of-multiplication-result.IgnoreConstantIntExpr: false
\end{lstlisting}

\item \cppid{bugprone-misplaced-widening-cast}:
Implicit conversions to wider types in calculations shall be avoided.

\item \cppid{bugprone-narrowing-conversions}:
Narrowing conversions leading to loss of informations shall be avoided.

\item \cppid{bugprone-switch-missing-default-case}:
A \cppkey{switch} statement shall always include a \cppkey{default} alternative.

\end{itemize}

\subsubsection{Excluded rules}

The following rules shall not be applied:

\begin{itemize}

\item \cppid{bugprone-argument-comment}.

\end{itemize}
