\subsection{Rules from C++ Core Guidelines}

All these rules are under category
\cppid{cppcoreguidelines}.

\subsubsection{Applicable rules}
Below, main applicable rules are described. Please, note that there are many
more rules from this category that are enabled. If you need a detailed
explanation, you can consult the clang-tidy manual.

\begin{itemize}

\item \cppid{cppcoreguidelines-avoid-const-or-ref-data-members}:
No data member shall be \cppkey{const} or reference type.

\item \cppid{cppcoreguidelines-avoid-do-while}:
No \cppkey{do-while} loop shall be used.

\item \cppid{cppcoreguidelines-avoid-goto}:
No \cppkey{goto} statement shall be used,
except to escape nested loops to a later statement.

\item \cppid{cppcoreguidelines-avoid-magic-numbers}:
No \emph{magic numbers} (numeric literals directly used in code)
shall be used. Instead, the corresponding constants will be defined
using \cppkey{constexpr}.

\item \cppid{cppcoreguidelines-avoid-non-const-global-variables}:
No global variable shall be defined unless it is a constant.

\textbad{Note}: The \emph{Singleton} design pattern shall not be used
to simulate a global variable.

\item \cppid{cppcoreguidelines-c-copy-assignment-signature}:
If the copy assignment operator is defined for a class, the following
rules shall be observed (for a class \cppid{X}):
  \begin{itemize}
    \item The return type shall be \cppid{X\&}.
    \item The \cppkey{return} statement shall always return \cppkey{*this}.
  \end{itemize}

\item \cppid{cppcoreguidelines-explicit-virtual-functions}:
When a \textmark{virtual function} is overriden qualifiers \cppkey{override}
and/or \cppkey{final} shall be used.

\item \cppid{cppcoreguidelines-init-variables}:
No local variable shall be defined without initializing it.

\item \cppid{cppcoreguidelines-interfaces-global-init}:
No global initialization shall be performed when they require access to
an external object.

\item \cppid{cppcoreguidelines-macro-to-enum}:
Instead of using macros to define a set of related constants,
enumerated types shall be used.

\item \cppid{cppcoreguidelines-macro-usage}:
No macro shall be used.

\item \cppid{cppcoreguidelines-narrowing-conversions}:
No \emph{narrowing conversion} shall be performed 
as they might potentially cause loss of information.
If needed, the library function \cppid{gsl::narrow<tipo>(valor)} from the 
\textemph{GSL} library shall be used for narrowing conversions.

\item \cppid{cppcoreguidelines-no-malloc}:
No invocation shall be performed to
\cppid{malloc()}, \cppid{realloc()}, \cppid{calloc()} or \cppid{free()}.

\item \cppid{cppcoreguidelines-noexcept-destructor}:
If a destructor is defined for a class, 
it will not be qualified as \cppkey{noexcept} 
or it will be qualified as unconditionally \cppkey{noexcept}.

\item \cppid{cppcoreguidelines-noexcept-move-operations}:
If move operations are defined, they will be qualified as 
\cppkey{noexcept}.

\item \cppid{cppcoreguidelines-noexcept-swap}:
If the \cppid{swap()} function is overloaded,
it will be uncondtionally qualified as \cppkey{noexcept}.

\item \cppid{cppcoreguidelines-owning-memory}:
If a pointer to memory that must be released is used, 
type \cppid{gsl::owner<T*>} shall be used.

\textbad{Note}: 
The use of smart pointers (such as \cppid{std::unique\_ptr<T>})
shall be preferred. Type \cppid{gsl::owner<T*>} shall only be used
when implementing very low level abstractions.

\item \cppid{cppcoreguidelines-prefer-member-initializer}:
In constructors, initialization sequence shall be preferred
instead of initialization in constructor body.

\item \cppid{cppcoreguidelines-slicing}:
Constructions leading to object slicing shall be avoided.
This situation happnes when an object of a derived class is copied into an
object of a base class.

\item \cppid{cppcoreguidelines-special-member-functions}:
If a copy operation, move operation or destructor is defined or deleted, 
all the other operations shall be defined or deleted.

\item \cppid{cppcoreguidelines-use-default-member-init}:
Data member initializers shall be preferred instead of initialization in the 
constructor, when both options are possible.

\item \cppid{cppcoreguidelines-virtual-class-destructor}:
A base class with a public destructor shall define it as \cppkey{virtual}.
If the destructor is protected, it shall be defined as non-\cppkey{virtual}.

\end{itemize}

\subsubsection{Specific rules on bounds checking}

\begin{itemize}

\item \cppid{cppcoreguidelines-pro-bounds-array-to-pointer-decay}:
Implicit conversion from arrays to pointers shall be avoided.
As an alternative, you may use
\cppid{std:span<T>} or \cppid{gsl::span<T>}.

\item \cppid{cppcoreguidelines-pro-bounds-constant-array-index}:
No access shall be performed to a primitive array or a \cppid{std::array}
with an expression whose value is unknown at compile time.
As an alternative, you may use 
\cppid{gsl::at()}.

\item \cppid{cppcoreguidelines-pro-bounds-pointer-arithmetic}:
No pointer arithmetic shall be used.

\end{itemize}

\subsubsection{Specific rules on type safety}

\begin{itemize}

\item \cppid{cppcoreguidelines-pro-type-const-cast}:
No \cppkey{const\_cast<>} shall be used to remove the \cppkey{const} qualifier
from an object.

\item \cppid{cppcoreguidelines-pro-type-cstyle-cast}:
No C-type \emph{cast} shall be used.

\item \cppid{cppcoreguidelines-pro-type-member-init}:
A constructor shall initialize any member that might otherwise be in an undefined state.

\item \cppid{cppcoreguidelines-pro-type-reinterpret-cast}:
No \cppkey{reinterpret\_cast<>} shall be used.

\item \cppid{cppcoreguidelines-pro-type-static-cast-downcast}:
No \cppkey{static\_cast<>} shall be used where
a \cppkey{dynamic\_cast} is considered more appropriate.

\item \cppid{cppcoreguidelines-pro-type-union-access}:
No access to unions shall be performed.

\textbad{Note}: 
In general, type \cppid{std::variant} should be used (insted of unions),
when variant record is needed.

\item \cppid{cppcoreguidelines-pro-type-vararg}:
No function with variable number of arguments via
\cppid{va\_arg} shall be used.

\end{itemize}

\subsubsection{Excluded rules}

The following rules shall not be applied:


\begin{itemize}

\item \cppid{cppcoreguidelines-non-private-member-variables-in-classes}

\end{itemize}

