\subsection{Misc rules}

All these rules are under category
\cppid{misc}.

\subsubsection{Applicable Rules}

The main applicable rules are summarized below. Please note that there are many more
rules in this category that are enabled. If you need a detailed explanation of any of them,
you can consult the \textemph{clang-tidy} manual.

\begin{itemize}

\item \cppid{misc-confusable-identifiers}:
Identifiers that are very similar and could cause confusion shall be avoided.

\item \cppid{misc-const-correctness}:
All variables that are initialized and not modified shall be defined as
\cppkey{const}.

\item \cppid{misc-definitions-in-headers}:
Variables will not be defined in header files unless they are qualified
with \cppkey{extern} or \cppkey{inline}.
Functions will not be defined in header files unless they are qualified
with \cppkey{inline}.

\item \cppid{misc-header-include-cycle}:
Cyclic dependencies among header files shall be avoided.

\item \cppid{misc-include-cleaner}:
Inclusion of not needed header files shall be avoided.

\item \cppid{misc-redundant-expression}:
Redundant expressions shall be avoided.

\item \cppid{misc-static-assert}:
When possible, \cppkey{static\_assert} shall be preferred over \cppid{assert}.

\item \cppid{misc-throw-by-value-catch-by-reference}:
Exceptions shall be thrown by value and caught by reference.

\item \cppid{misc-use-anonymous-namespace}:
Placing a function or a variable in an \textmark{anonymous namespace} will be
preferred over defining them as \cppkey{static}.

\end{itemize}

\subsubsection{Excluded Rules}

The following rules shall not be applied:

\begin{itemize}

\item \cppid{misc-no-recursion}.
\item \cppid{misc-non-private-member-variables-in-classes}.
\item \cppid{misc-use-internal-linkage}.

\end{itemize}
