\subsection{Rules on Readability}

All these rules are found under the \cppid{readability} category.

\subsubsection{Applicable Rules}

The main applicable rules are summarized below. Please note that there are many more
rules in this category that are enabled. If you need a detailed explanation of any of them,
you can consult the \textemph{clang-tidy} manual.

\begin{itemize}

\item \cppid{readability-avoid-const-params-in-decls}:
\cppkey{const} type parameters shall not be allowed in function declarations.
\cppkey{const} reference parameters shall be allowed.

\item \cppid{readability-avoid-nested-conditional-operator}:
The nested use of the conditional operator (\cppkey{?:}) shall not be allowed.

\item \cppid{readability-braces-around-statements}:
The body of \cppkey{if}, \cppkey{while}, and \cppkey{for} statements shall
always be enclosed in braces, even if it is a single statement.

\item \cppid{readability-const-return-type}:
The return type of a function shall not include the \cppkey{const} qualifier.

\item \cppid{readability-convert-member-functions-to-static}:
Member functions that do not use any non-static members shall be qualified as
\cppkey{static}.

\item \cppid{readability-duplicate-include}:
The duplicate inclusion of header files shall be avoided.

\item \cppid{readability-else-after-return}:
Constructs \cppkey{else} or \cppkey{else if} shall not be used after control flow interruptions
(\cppkey{return}, \cppkey{break}, \cppkey{continue}, or \cppkey{throw}).

\item \cppid{readability-function-cognitive-complexity}:
The maximum cognitive complexity shall be \cppid{50}.

The following options shall be used:

\begin{lstlisting}
readability-function-cognitive-complexity.Threshold: 50
readability-function-cognitive-complexity.Threshold.DescribeBasicIncrements: true
\end{lstlisting}

\item \cppid{readability-function-size}:
The maximum number of lines per function shall be \cppid{40}.
The maximum number of parameters per function shall be \cppid{4}.

The following options shall be used:

\begin{lstlisting}
readability-function-size.LineThreshold: 40
readability-function-size.ParameterThreshold: 4
\end{lstlisting}

\item \cppid{readability-magic-numbers}:
\emph{Magic numbers} shall not be used in the code.
Instead, appropriate constants shall be defined.

\item \cppid{readability-make-member-function-const}:
If a member function does not modify the object's state, it shall be marked as \cppkey{const}.

\item \cppid{readability-operators-representation}:
The use of alternate tokens for logical and bitwise operators shall be preferred:
\cppkey{and}, \cppkey{and\_eq}, \cppkey{bitand}, \cppkey{bitor}, \cppkey{compl},
\cppkey{not}, \cppkey{not\_eq}, \cppkey{or}, \cppkey{or\_eq}, \cppkey{xor},
\cppkey{xor\_eq}.

The following options shall be applied:

\begin{lstlisting}
readability-operators-representation.BinaryOperators: 'and;and_eq;bitand;bitor;or;or_eq;xor;xor_eq'
readability-operators-representation.OverloadedOperators: 'and;and_eq;bitand;bitor;or;or_eq;xor;xor_eq'
\end{lstlisting}

\end{itemize}

\subsubsection{Excluded Rules}

The following rules shall not be applied:

\begin{itemize}

\item \cppid{readability-enum-initial-value}.
\item \cppid{readability-identifier-length}.
\item \cppid{readability-identifier-naming}.
\item \cppid{readability-isolate-declaration}.
\item \cppid{readability-math-missing-parentheses}.
\item \cppid{readability-named-parameter}.
\item \cppid{readability-redundant-access-specifiers}.

\end{itemize}
